---
title: "Assignment_3_2R_Yuan12575275"
author: "Luiza Yuan"
date: "1/27/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q3.2R.1

### remind_me() function
remind_me() takes no arguments and returns some things that are useful for you to remember
```{r}
remind_me <- function(){
  Name <- c("Mom", "Kai", "Dad", "Laura", "Lola")
  Birthday <- c("22-01-1963", "30-01-1994", "02-02-1954", "06-02-1997","10-02-1995")
  Birthdays <- data.frame(Name, Birthday)
  To_do <- c("Rene research proposal pitch", "ManyBabies lab meeting prep", "Basic Skills preparation")
  Deadline <- c("Jan 30th", "Feb 2nd", "Feb 6th")
  Deadlines <- data.frame(To_do, Deadline)
  print("These are your reminders for today:")
  print(Birthdays)
  print(Deadlines)
}

remind_me()
```

### cheat() function
cheat() takes one argument specifying which exercise from assignment 3.1. The user of your package wants to cheat on. Given the exercise number, your cheat() function tells the user the correct solution. 
```{r}
cheat <- function(exercise){
  if(exercise == "Q3.1.3"){
    library(ggplot2) #load ggplot2
    library(titanic) #load titanic
    
    titanic <- titanic_train
    head(titanic) #inspect passenger data
    
    titanic$Survived[titanic$Survived == 0] <-
      "dead" #assign "dead" to Survived == 0
    titanic$Survived[titanic$Survived == 1] <-
      "alive" #assign "alive" to Survived == 1
    
    Q3_plot <-
      ggplot(data = titanic, aes(x = Sex, fill = factor(Survived, levels = c("dead", "alive")))) +
      geom_bar(position = "stack") + labs(fill = "How did it go?") 
    return(Q3_plot)
  }
  if(exercise == "Q3.1.6"){
    max_weight_chick <-
      aggregate(ChickWeight$weight, by = list(Chick = ChickWeight$Chick), max) 
    max_weight_chick <-
      max_weight_chick[max_weight_chick$Chick %in% c(1, 20, 3, 40, 5), ] 
    
    max_weight_chick$Chick <-
      factor(max_weight_chick$Chick, levels = c(1, 20, 3, 40, 5)) 
    Q6_plot <-
      ggplot(data = max_weight_chick, aes(x = Chick, y = x)) + geom_bar(stat = "identity") + xlab("chick") + ylab("max_weight") # Plot the bar graph with geom_bar
    return(Q6_plot)
  }
  if(exercise == "Q3.1.10"){
    library(plotly)
    Q10_data <- read.csv("Body Measurements.csv")
    
    Q10_plot <-
      plot_ly(
        Q10_data,
        x = ~ TotalHeight,
        y = ~ LegLength,
        z = ~ ShoulderToWaist
      ) #create a 3D scatter plot
    return(Q10_plot)
  }
  if(exercise == "Q3.1.12"){
    library(quantmod) #load package

    Sys.setenv(TZ = "UTC") 
    getSymbols("IBM", from = "2022-01-1", to = "2022-12-31") 
    
    Q12_plot <-
      chartSeries(
        IBM,
        type = "bars",
        show.grid = TRUE,
        bar.type = "hlc",
        theme = chartTheme("white")
      )
    return(Q12_plot) #plot price of IBM stock in 2022 using chart_Series function
  }
  if(exercise == "Q3.1.13"){
    plotstock <-
      function(stock = "IBM",
               year = "2022",
               file = "plotstock_IBM") {
        start <- paste(year , "-01-1", sep = "")
        end <- paste(year , "-12-31", sep = "")
        stock_data <-
          getSymbols(
            Symbols = stock,
            env = .GlobalEnv,
            from = start,
            to = end,
            auto.assign = FALSE
          )
        file_name <- paste(file , ".jpeg", sep = "")
        jpeg(file = file_name)
        stock_plot <- chartSeries(
          stock_data,
          type = "bars",
          show.grid = TRUE,
          name = stock,
          bar.type = "hlc",
          theme = chartTheme("white")
        )
        dev.off()
      }
    return(plotstock()) #run function
  }
}

#example
cheat("Q3.1.10")
```

## Q3.2R.1

### Make_art() function 
The following function takes a random seed as an argument and produces random art. 
```{r}
library(RColorBrewer)
library(ggplot2)

make_art <- function(seed) {
  set.seed(seed)
  data <- data.frame(x = runif(1000, min = -100, max = 100) + runif(5, min = -100, max = 100),
                     y = runif(1000, min = -100, max = 100) + runif(5, min = -100, max = 100),
                     color = sample(brewer.pal(n = 8, name = "Dark2"), 1000, replace = TRUE))
  ggplot(data, aes(x, y, color = color)) +
    geom_line(aes(group = cut_number(..x.., 5), fill = color),alpha = 0.8) +
    geom_path(aes(group = cut_number(..x.., 5)), size = 0.5) +
    theme_void() +
    theme(legend.position = "none")
}
```

### Examples of random art produced:
```{r}
#seed argument = 12
make_art(12)

#seed argument = 17
make_art(17)

#seed argument = 120
make_art(120)
```
